An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-22 neurips-19/poly-embed.tex

We write the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.

When embedding, we consider the discrete loss
\begin{align*}
\ell_2(r,y) &= \Ind[y \not\in r] + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)~,~
\end{align*}
and claim that $L_2$ embeds $\ell_2$.  
(3.) Finally, taking $k = 1$, we see that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.

@@

	For the first case, we claim that $e_y \in \argmin_{u \in [0,1]^n} \inprod{p}{L_2(u)}$.
	Consider
	\begin{align*}
		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
		&= \frac{k+1}{k} (1 - p_y) + 0 \\
		&\leq \frac{k+1}{2k} \\
		&\leq 1
	\end{align*}
	\jessie{TODO-- brain is fried and giving up for the night.}

>>>>

We write the surrogate $L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
$L_2$ is a polyhedral loss, since it can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \indopp(y)$ with highest weight.
By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L_2}$ is also polyhedral.

When embedding, we consider the discrete loss
\begin{align*}
\ell_2(r,y) &= \Ind[y \not\in r] + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)~,~
\end{align*}
and claim that $L_2$ embeds $\ell_2$.

Finally, taking $k = 1$, we see that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$, while the expected loss for $\ell_{top-k}$ is strictly less when predicting $\argmax_y p_y$.

@@

	For the first case, we claim that $e_y \in \argmin_{u \in [0,1]^n} \inprod{p}{L_2(u)}$.
	Consider
	\begin{align*}
		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
		&= \frac{k+1}{k} (1 - p_y) %+ 0 \\
%		&\leq \frac{k+1}{2k} \\
%		&\leq 1
	\end{align*}
	\jessie{TODO-- Not sure how.  Two thoughts: can we leverage Jensen's inequality since we have convexity?  Or can we show these are supporting hyperplanes of the risk?}
